Generality in food webs scales with species richness, not latitude

### 2015-01-28 manuscript/latitudepaper.tex
updated results

\begin{eqnarray}
S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \epsilon_{i} 
\end{eqnarray}

where $S_{i}$ is the species richness of web $i$, $\Lambda_{i}$ its absolute latitude (degrees north or south 
regardless of direction), and $\epsilon_{i}$ a residual error term.
These simple linear models, fit using the function lm in R \citep{R} package stats, were used to confirm that there are indeed latitudinal gradients in food-web structure in this data set.

@@

Contrary to expected latitudinal gradients, $S$ and $G$ both increased with increasing latitude(Table \ref{Latlms}). 
$G$ and $V$ were not significantly correlated with latitude.

@@

\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Slope} \\
                      & $\alpha_{0}$ & $p$-value & $\alpha_{1}$ & $p$-value \\
\hline
$S$ & 23.10 & \textless0.001 & 0.284 & 0.040 \\
$Z$ & 2.566 & \textless0.001 & 0.020 & 0.180 \\
$G$ & 3.269 & \textless0.001 & 0.049 & 0.014 \\
$V$ & 2.566 & \textless0.001 & 0.020 & 0.180 \\
\end{tabular}
\end{table}

@@

The effect of latitude on scaling relationships varied across ecosystem types (Table~\ref{Bestfits}). 
In lakes and streams, the scaling exponent for species richness increased with latitude (although this 
increase was not significant for lakes and generality). For other types of ecosystems, the scaling 
exponent for species richness did not change significantly with latitude. 
[[Some more description after figures.]]

@@

\caption{Standard effects and their $p$-values for the best-fitting models of links per species ($Z$), generality ($G$), and vulnerability ($V$).}
\label{Bestfits}
\begin{tabular}{l | l l | l l | l l }
\multirow{2}{*}{Effect} & \multicolumn{2}{c}{$Z$} & \multicolumn{2}{c}{$G$} & \multicolumn{2}{c}{$V$}\\
                & $\beta$ & $p$-value &  $\beta$ & $p$-value &  $\beta$ & $p$-value & \\
\hline
Intercept               & -0.561 & \textless0.001 & -0.299 & \textless0.001 & -0.561 & \textless0.001 \\
log(species)            &  0.733 & \textless0.001 &  0.622 & \textless0.001 &  0.733 & \textless0.001 \\
log(species):Lake       & -0.118 & 0.047          & -0.115 & 0.078          & -0.118 & 0.047 \\
log(species):Marine     &  0.051 & 0.040          &  0.120 & \textless0.001 &  0.051 & 0.040 \\
log(species):Stream     & -0.161 & 0.014          & -0.057 & 0.421          & -0.161 & 0.014 \\
log(species):Latitude   & -0.001 & 0.081          & -0.001 & 0.273          & -0.001 & 0.081 \\
log(species):Lat:Lake   &  0.006 & \textless0.001 &  0.006 & \textless0.001 &  0.006 & \textless0.001 \\
log(species):Lat:Stream &  0.004 & 0.018          &  0.003 & 0.059          &  0.004 & 0.018 \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{eqnarray}
S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} 
\end{eqnarray}

where $S_{i}$ is the species richness of web $i$, $\Lambda_{i}$ its absolute
latitude (degrees north or south  regardless of direction), $E_{i}$ is the
ecosystem type of network $i$ and $\epsilon_{i}$ a residual error term. If the
interaction between latitude and ecosystem type was not significant, this term
was removed and the model re-fit. These simple linear models, fit using the
function lm in R \citep{R} package stats, were used to determine whether there
were latitudinal gradients in food-web structure in this data set.

@@

Contrary to expected latitudinal gradients, $S$, $Z$, $G$ and $V$ did not vary significantly over latitude, although $S$ and $G$ did vary over ecosystem types (Table~\ref{Latlms}, Fig.~\ref{Latfigs}).

@@

\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Slope} \\
                      & $\alpha_{0}$ & $p$-value & $\alpha_{1}$ & $p$-value \\
\hline
$S$ & 29.42 & \textless0.001 & 0.188 & 0.167 \\
$Z$ & 2.724 & 0.002          & 0.017 & 0.283 \\
$G$ & 3.095 & 0.006          & 0.035 & 0.080 \\
$V$ & 2.724 & 0.002          & 0.017 & 0.283 \\
\end{tabular}
\end{table}

@@

The effect of latitude on scaling relationships varied across ecosystem types
(Table~\ref{Bestfits}, Fig.~\ref{scalingfig}).  In lakes and streams, the
scaling exponent for species richness increased with latitude (although this
increase was not significant for lakes and generality). For other types of
ecosystems, the scaling  exponent for species richness decreased, but not significantly,
with latitude. Despite these overal trends, the observed networks displayed a great deal
of variability in each property.

@@

\caption{Standard effects and their $p$-values for the best-fitting models of links per species ($Z$), generality ($G$), and vulnerability ($V$).}
\label{Bestfits}
\begin{tabular}{l | l l | l l | l l }
\multirow{2}{*}{Effect} & \multicolumn{2}{c}{$Z$} & \multicolumn{2}{c}{$G$} & \multicolumn{2}{c}{$V$}\\
                & $\beta$ & $p$-value &  $\beta$ & $p$-value &  $\beta$ & $p$-value & \\
\hline
Intercept               & -0.561 & \textless0.001 & -0.299 & \textless0.001 & -0.561 & \textless0.001 \\
log(species)            &  0.733 & \textless0.001 &  0.622 & \textless0.001 &  0.733 & \textless0.001 \\
log(species):Lake       & -0.118 & 0.047          & -0.115 & 0.078          & -0.118 & 0.047 \\
log(species):Marine     &  0.051 & 0.040          &  0.120 & \textless0.001 &  0.051 & 0.040 \\
log(species):Stream     & -0.161 & 0.014          & -0.057 & 0.421          & -0.161 & 0.014 \\
log(species):Latitude   & -0.001 & 0.081          & -0.001 & 0.273          & -0.001 & 0.081 \\
log(species):Lat:Lake   &  0.006 & \textless0.001 &  0.006 & \textless0.001 &  0.006 & \textless0.001 \\
log(species):Lat:Stream &  0.004 & 0.018          &  0.003 & 0.059          &  0.004 & 0.018 \\
\hline
$R^{2} (adjusted)$   & \multicolumn{2}{c}{0.706} & \multicolumn{2}{c}{0.658} & \multicolumn{2}{c}{0.706} \\
\end{tabular}
\end{table}
